IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/real.tex
real

We have implemented |specLangJS seqf| for Node.js in the form of a module
(library), which does not modify the Node.js or V8 code-base in any
way.
%
Our implementation provides a library for creating new tasks, i.e.,
contexts whose global object only contains the standard JavaScript
library as well as our IFC primitives (such as |send| and |sandbox|).
%
In turn, these tasks can create new tasks with |sandbox|.
%
In our formal treatement, |sandbox| is defined with |ap klone tS = tS0|,
where |tS0| is the global object corresponding to the standard
JavaScript library and our IFC primitives.

@@

While the described system implements |specLangJS seqf|, server-side
applications may require access to the file system, HTTP server, HTTP
client, etc.
%
Unfortunately, our formalism does not capture such external effects
and exposing the Node.js libraries directly to sandboxed tasks is unsafe.
%
We, instead, implement libraries such as a labeled file system as
message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
in Figure~\ref{fig:node}) and the main Node.js task that implements
our IFC monitor.\footnote{
  Importantly, we provide mostly-identical interfaces to
  the standard Node.js libraries, hiding the underlying
  message-passing implementations.
}
%
(This is safer than the approach of simply wrapping objects, which can
potentially allow objects to be accessed outside the context.)
%
This task is trusted to ensures that labels are
propagated to files and the labels of the task and the file in question permit
this flow.
%
Unfortunately, while imposing such a proof burden on the
framework developer is undesirable, this is also somewhat expected:
different language environments expose different libraries for
handling external I/O.
%
For instance, in the case of Node.js, how labels interact with the
file system may even vary according to the application (e.g.,
in the IFC system Hails~\cite{hails}, labels are not persisted).
%
While we can extend our formalism to model a particular interface to
the file system, HTTP client, etc. the utility of this formalization is
unclear and left to future work.
%

@@

\subsection{Haskell}
\label{sec:real:hs}
Our work borrows many ideas from the Haskell coarse-grained IFC
system LIO~\cite{lio, stefan:addressing-covert}.
%
LIO relies on Haskell's strong type system and monadic encoding of
side-effecting computations to achieve isolation and define the IFC
sub-language.
%
Specifically LIO provides the \verb|LIO| monad as a way of restricting
(almost all) side-effects; this monad also keeps track of a current
label which is, in turn, used by trusted code when defining core IFC
functions, such as |getLabel|.
%
In the context of our framework, LIO can be understood as follows: the
\emph{pure subset} of Haskell is the target language, while the
monadic subset of Haskell, operating in the \verb|LIO| monad, is the
IFC language.

Indeed, by rephrasing LIO in terms of our framework, we simplified
LIO's treatment of exceptions.
%
LIO originally associated labels with exceptions, in a
similar style to fine-grained
systems~\cite{stefan:2012:arxiv-flexible, Hritcu:2013:YIB:2497621.2498098}.
%
In particular, the label of an exception was set to the current label
at the time of the throw, and used by a custom catch construct to
raise the current label, thereby preventing leaks due exceptional
control flows.
%
In addition to being overly complex, the interaction of exceptions
with clearance (which sets an upper bound on the current label, see
Section~\ref{sec:clearance}) was incorrect: the clearance
was restored to the clearance at point of the catch (a consequence of
defining \verb|LIO| using a State monad).
%
Moreover, pure exceptions (e.g., divide by zero) always percolated to
trusted code, effectively allowing for denial of service attacks.
%
By using isolated tasks, and thus treating the current label (and
clearance) as global, the underlying Haskell exception system can be
used directly: exceptional control flow does not affect IFC.

>>>>

We have implemented |specLangJS seqf| for Node.js in the form of a module
(library), which does not modify the Node.js or V8 code-base in any
way.
%
Our implementation\footnote{The source code of our implementation can be found at
  \codelink{}.} provides a library for creating new tasks, i.e.,
contexts whose global object only contains the standard JavaScript
library as well as our IFC primitives (such as |send| and |sandbox|).
%
In turn, these tasks can create new tasks with |sandbox|.
%
In our formal treatement, |sandbox| is defined with |ap klone tS = tS0|,
where |tS0| is the global object corresponding to the standard
JavaScript library and our IFC primitives.

@@

While the described system implements |specLangJS seqf|, server-side
applications may require access to the file system, HTTP server, HTTP
client, or other APIs that have external effects.
%
Exposing the Node.js APIs directly to sandboxed tasks is unsafe, and
thus we
%
instead implement libraries such as a labeled file system as
message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
in Figure~\ref{fig:node}) and the main Node.js task that implements
our IFC monitor.\footnote{
  Importantly, we provide mostly-identical interfaces to
  the standard Node.js libraries, hiding the underlying
  message-passing implementations.
}
%
This is safer than the approach of simply wrapping objects, which can
potentially allow objects to be accessed outside the context.
%
This task is trusted to ensures that labels are
propagated to files and the labels of the task and the file in question permit
this flow.
%
Unfortunately, while imposing such a proof burden on the
framework developer is undesirable, this also has to be expected:
different language environments expose different libraries for
handling external I/O, and the correct treatment of external effects
is application specific.
%
For instance, in the case of Node.js, how labels interact with the
file system may even vary according to the application (e.g.,
in the IFC system Hails~\cite{hails}, labels are not persisted).
%
%While we can extend our formalism to model a particular interface to
%the file system, HTTP client, etc. the utility of this formalization is
%unclear and left to future work.
%

@@

\subsection{Haskell}
\label{sec:real:hs}
Our work borrows ideas from a Haskell coarse-grained IFC
system called LIO~\cite{lio, stefan:addressing-covert}.
%
LIO relies on Haskell's strong type system and monadic encoding of
side-effecting computations to achieve isolation and define the IFC
sub-language.
%
Specifically LIO provides the \verb|LIO| monad as a way of restricting
(almost all) side-effects; this monad also keeps track of a current
label which is, in turn, used by trusted code when defining core IFC
functions, such as |getLabel|.
%
In the context of our framework, LIO can be understood as follows: the
\emph{pure subset} of Haskell is the target language, while the
monadic subset of Haskell, operating in the \verb|LIO| monad, is the
IFC language.

%Indeed, by rephrasing LIO in terms of our framework, we simplified
%LIO's treatment of exceptions.
%
LIO originally associated labels with exceptions, in a
similar style to fine-grained
systems~\cite{stefan:2012:arxiv-flexible, Hritcu:2013:YIB:2497621.2498098}.
%
In particular, the label of an exception was set to the current label
at the time of the throw, and used by a custom catch construct to
raise the current label, thereby preventing leaks due to exceptional
control flows.
%
In addition to being overly complex, the interaction of exceptions
with clearance (which sets an upper bound on the current label, see
Section~\ref{sec:clearance}) was incorrect: the clearance
was restored to the clearance at point of the catch (a consequence of
defining \verb|LIO| using a State monad).
%
Furthermore, pure exceptions (e.g., divide by zero) always percolated to
trusted code, effectively allowing for denial of service attacks.
%
The insights gained when viewing coarse-grained IFC as presented in this
paper led to a much cleaner, simpler treatment of exceptions in LIO,
which has now been adapted by LIO.
%By using isolated tasks, and thus treating the current label (and
%clearance) as global, the underlying Haskell exception system can be
%used directly: exceptional control flow does not affect IFC.
